---
title: "Merged"
author: "Asmer Asrar Safi"
date: "2/22/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(hrbrthemes)
library(ggrepel)
library(ggthemes)
library(viridis)
library(fmsb)
library()
library(ggridges)
library(skimr)
library(tidyverse)

 options(scipen = 999)
```

```{r}

# per-capita GDP: WB_ny_gdp_pcap_pp_cd. Filtering merged data (with GDP per capita) to create 3 subsets of data: merged_18 has all of the countries' data for 2018. merged_bm has all of the comparator countries' data for 2018. merged_pak is just Pakistan's data for 2018. 

merged_18 <- Uzair_Data_Merged %>% 
  filter(Year == 2018)

merged_bm <- merged_18 %>% 
  filter(Country %in% c("IND", 
                        "BGD",
                        "TUR",
                        "VNM", 
                        "NPL", 
                        "ZMB",
                        "KEN", 
                        "CHN", 
                        "MAR", 
                        "LAO"))

 colorz <- c("dodgerblue4", #BGD
             "red", #CHN
             "darkorange", #IND
             "darkorchid3", #KEN
             "pink", #LAO
             "darkblue", #MAR
             "skyblue3", #NPL
             "darkred", #TUR
             "turquoise", #VNM
             "yellowgreen") #ZMB

merged_pak <- merged_18 %>% 
  filter(Country == "PAK")

merged_18
```

```{r}
# What graphs do we want to make? 1) Ecommerce mobile on Y-axis and most important variables (as determined by Random Forest) on the X-axis. 2) GDP per capita on X-Axis and Important variable penetration on Y-Axis

# Current problem: Even though we now have GDP per capita, we still need to be able to write it in factors of 10 at max. Need to figure this out. 

# Also have to make Spider Charts. 

```

```{r}

# GDP per capita and important variable. Save labels for future use. 

```

Variables from Random Forest:

ecom_mbl – Mobile E-Commerce Retail Value (% of total Retail)
brdbd – Fixed broadband subscriptions per 100 inhabitants
mtravl – Mobile Online Travel Sales

servr – Secure Internet Servers per 1 million people (WB_ny_gdp_pcap_pp_cd, servr), (GDP per capita and Secure Internet Servers)

egovi – E-Government Development Index
avgbw – Average Bandwidth Connection Speed in Kilobytes per second
apps – Apps developed per person
mbl_access – Use of a Mobile Phone to Access the Internet (% of Population)
rdexp – Research and Development Expenditure
mdply – Made digital payments in the last year (15+)
download_gsma – Mobile download speeds
cpvpc – Card Payment Value per capita (% of transaction value)
dispi – Disposable Income per capita
mobilie_f_gap – Gender gap in mobile ownerships
gov_mbl – Government transfers made through 
retail – Retail value
hhi_gsma – HH Index
hset_price – Handset price
middle – Middle Class Households (percentage of total)
smart – Smartphone possession 

WB_ny_gdp_pcap_pp_cd - per capita GDP. 


## GRAPH FOR GDP and VARIABLE

```{r}

merged_18 %>%  
  ggplot(aes(WB_ny_gdp_pcap_pp_cd, servr)) +
  geom_point(color = "darkgrey", alpha = 0.6, size = 2.5)  +
  scale_y_log10() +
  geom_smooth(aes(WB_ny_gdp_pcap_pp_cd, servr), method = "lm", se = FALSE, size = 0.5, linetype = "dashed") +
  theme_minimal() +
  geom_point(data = merged_bm, aes(WB_ny_gdp_pcap_pp_cd, servr), color = "skyblue2", alpha = 0.6, color = "black", size = 2.5) +
  geom_point(data = merged_pak, aes(WB_ny_gdp_pcap_pp_cd, servr), color = "darkgreen",  color = "black", size = 2.5) +
  geom_label_repel(data = merged_pak,
                  aes(WB_ny_gdp_pcap_pp_cd, servr, label = "PAK"),
                  box.padding   = 0.6,
                  point.padding = 0.3,
                  # label.size = 0.15,
                  # min.segment.length = 6,
                   segment.color = 'black',
                  color = 'darkgreen') +
  labs(x = "Log of Per Capita GDP PPP",
       y = "Secure Internet Servers per 1 million people",
       title = "GDP per capita and Secure Internet Servers",
       subtitle = "Year: 2018",
       caption = "Data: Euromonitor") +
  theme(axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8),
        plot.title = element_text(face = "bold",
                                    size = 10,
                                    hjust = 0.5),
        plot.subtitle = element_text(size = 10,
                                     hjust = 0.5),
        plot.caption =  element_text(face = "italic",
                                      hjust = 0.5,
                                      size = 8)) +
    scale_x_continuous()+
    scale_x_log10(breaks = c(1000, 10000, 100000),
                  labels = c(1, 10, 100)) 



```

# GDP and variable with colored benchmark



```{r}
merged_18 %>%  
  ggplot(aes(WB_ny_gdp_pcap_pp_cd, servr)) +
  geom_point(color = "darkgrey", alpha = 0.6, size = 2.5)  +
  scale_y_log10() +
  geom_smooth(aes(WB_ny_gdp_pcap_pp_cd, servr), method = "lm", se = FALSE, size = 0.5, linetype = "dashed") +
  theme_minimal() +
  geom_point(data = merged_bm, aes(WB_ny_gdp_pcap_pp_cd, servr, color = Country), alpha = 0.6, size = 2.5) +
  geom_point(data = merged_pak, aes(WB_ny_gdp_pcap_pp_cd, servr), shape = 22, size = 3, fill = "darkgreen",  color = "black", size = 2.5) +
  geom_label_repel(data = merged_pak,
                   size = 3,
                  aes(WB_ny_gdp_pcap_pp_cd, servr, label = "PAK"),
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  segment.color = 'black',
                  color = 'darkgreen') +
  labs(x = "Log of Per Capita GDP PPP",
       y = "Secure Internet Servers per 1 million people",
       title = "GDP per capita and Secure Internet Servers",
       subtitle = "Year: 2018",
       caption = "Data: Euromonitor") +
  theme(axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8),
        plot.title = element_text(face = "bold",
                                    size = 10,
                                    hjust = 0.5),
        plot.subtitle = element_text(size = 10,
                                     hjust = 0.5),
        plot.caption =  element_text(face = "italic",
                                      hjust = 0.5,
                                      size = 8)) +
    scale_x_continuous()+
    scale_x_log10(breaks = c(1000, 10000, 100000),
                  labels = c(1, 10, 100)) +
  scale_color_manual(values = colorz)



```



## GRAPH FOR ECOM AND VARIABLE

```{r}


 merged_18 %>% 
  ggplot(aes(dispi, ecom)) +
  geom_point(color = "darkgrey", alpha = 0.6, size = 2.5)  +
  geom_smooth(aes(dispi, ecom), method = "lm", se = FALSE, size = 0.5, linetype = "dashed") +
  theme_minimal() +
  geom_point(data = merged_bm, aes(dispi, ecom, color = Country), alpha = 0.6, size = 2.5) +
  geom_point(data = datapak18, aes(dispi, ecom), shape = 22, size = 3, fill = "darkgreen",  color = "black", size = 2.5) +
  geom_label_repel(data = merged_pak,
                   size = 3,
                  aes(dispi, ecom, label = "PAK"),
                  box.padding   = 0.8,
                  point.padding = 0.3,
                   segment.color = 'black',
                  color = 'darkgreen') +
  labs(x = "Disposable Income Per Capita (USD)",
       y = "Mobile E-Commerce Retail Value (% total retail value)",
       title = "Disposable Income and E-Commerce Retail Value",
       subtitle = "Year: 2018",
       caption = "Data: Euromonitor") +
  theme(axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8),
        plot.title = element_text(face = "bold",
                                    size = 10,
                                    hjust = 0.5),
        plot.subtitle = element_text(size = 10,
                                     hjust = 0.5),
        plot.caption =  element_text(face = "italic",
                                      hjust = 0.5,
                                      size = 8)) +
  scale_color_manual(values = colorz) +
  scale_x_log10()

```

# From multi-way importance plot (Random Forest) we get 5 most important variables: ecom_mbl, avgbw, servr, brdbd, smart

# Plotting graphs for both them with ecom (E-Commerce Retail Value (% total retail value)) and per capita GDP. 

```{r}
# ecom_mbl

# GDP
merged_18 %>%  
  ggplot(aes(WB_ny_gdp_pcap_pp_cd, midle)) +
  geom_point(color = "darkgrey", alpha = 0.6, size = 2.5)  +
  # scale_y_log10() +
  geom_smooth(aes(WB_ny_gdp_pcap_pp_cd, midle), method = "lm", se = FALSE, size = 0.5, linetype = "dashed") +
  theme_minimal() +
  geom_point(data = merged_bm, aes(WB_ny_gdp_pcap_pp_cd, midle, color = Country), alpha = 0.6, size = 2.5) +
  geom_point(data = merged_pak, aes(WB_ny_gdp_pcap_pp_cd, midle), shape = 22, size = 3, fill = "darkgreen",  color = "black", size = 2.5) +
  geom_label_repel(data = merged_pak,
                   size = 3,
                  aes(WB_ny_gdp_pcap_pp_cd, midle, label = "PAK"),
                  box.padding   = 0.5,
                  point.padding = 0.5,
                  segment.color = 'black',
                  color = 'darkgreen') +
  labs(x = "Log of Per Capita GDP PPP",
       y = "Middle Class Households (% of Total)",
       title = "GDP per capita and Middle Class Households",
       subtitle = "Year: 2018",
       caption = "Data: GSMA") +
  theme(axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8),
        plot.title = element_text(face = "bold",
                                    size = 10,
                                    hjust = 0.5),
        plot.subtitle = element_text(size = 10,
                                     hjust = 0.5),
        plot.caption =  element_text(face = "italic",
                                      hjust = 0.5,
                                      size = 8)) +
    scale_x_continuous()+
    scale_x_log10(breaks = c(1000, 10000, 100000),
                  labels = c(1, 10, 100)) +
  scale_color_manual(values = colorz)

```

# E-Commerce Retail Value (% total retail value)

```{r}

 merged_18 %>% 
  ggplot(aes(mobile_f_gap, ecom)) +
  geom_point(color = "darkgrey", alpha = 0.6, size = 2.5)  +
  geom_smooth(aes(mobile_f_gap, ecom), method = "lm", se = FALSE, size = 0.5, linetype = "dashed") +
  theme_minimal() +
  geom_point(data = merged_bm, aes(mobile_f_gap, ecom, color = Country), alpha = 0.6, size = 2.5) +
  geom_point(data = datapak18, aes(mobile_f_gap, ecom), shape = 22, size = 3, fill = "darkgreen",  color = "black", size = 2.5) +
  geom_label_repel(data = merged_pak,
                   size = 3,
                  aes(mobile_f_gap, ecom, label = "PAK"),
                  box.padding   = 0.8,
                  point.padding = 0.3,
                   segment.color = 'black',
                  color = 'darkgreen') +
  labs(x = "Gender gap in mobile ownership",
       y = "E-Commerce Retail Value (% total retail value)",
       title = "Gender gap in mobile ownership and \n E-Commerce Retail Value (% of total retail value)",
       subtitle = "Year: 2018",
       caption = "Data: GSMA") +
  theme(axis.title.x = element_text(size = 8), 
        axis.title.y = element_text(size = 8),
        plot.title = element_text(face = "bold",
                                    size = 10,
                                    hjust = 0.5),
        plot.subtitle = element_text(size = 10,
                                     hjust = 0.5),
        plot.caption =  element_text(face = "italic",
                                      hjust = 0.5,
                                      size = 8)) +
  scale_color_manual(values = colorz)
```


```{r}
merged_18
```






